Title Goes Here

### 2020-02-25 paper/paper.tex
Switched Oxford brackets to parens
Using a slightly more common rewrite notation

\newcommand{\expr}[1]{\llbracket#1\rrbracket} % Oxford brackets
\newcommand{\rarr}{\rightarrow}
\newcommand{\Rarr}{\Rightarrow}

@@

\begin{tcolorbox}
  \textbf{TODO}: Does this subsection use Oxford brackets in an appropriate way?
\end{tcolorbox}

\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &:= \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}
\end{align*}

\begin{align*}
  T'_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ case s of \{ ...$_A$ \}; ...$_B$ \}}}\\
    &:=
        \ttt{\{ K x0 ... xN $\rarr$ $T_{\ttt{f}}\expr{\ttt{case s of \{ ...$_A$ \}}}$; $T'_{\ttt{f}}\expr{\ttt{\{ ...$_B$ \}}}$\}}\\
  T'_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}}\\
    &:=
      \begin{cases}
        \ttt{\{ K x0 ... xN $\rarr$ body}[\ttt{f} \mapsto \ttt{Step}]\ttt{; }T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}\ttt{ \}} & \text{if \ttt{f} occurs free in \ttt{body}}\\
        \ttt{\{ K x0 ... xN $\rarr$ Done body; ... \}} & \text{otherwise}
      \end{cases}\\
  T'_{\ttt{f}}&\expr{\ttt{\{ \}}} := \ttt{\{ \}}\\
  T_{\ttt{f}}&\expr{\ttt{case s of \{ ... \}}}\\
    &:=
      \begin{cases}
        \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{Done (case s of \{ ... \})} & \text{otherwise}
      \end{cases}
\end{align*}
\begin{align*}
  &C^{*}\expr{\ttt{x}} :=
    \begin{cases}
      \ttt{x} & \text{if \ttt{x} has no subexpressions marked with \ttt{externalize}}\\
      C^{*}\expr{C\expr{\ttt{y}}} & \text{if \ttt{externalize y} is the first marked subexpression of \ttt{x}}\\
    \end{cases}\\
\end{align*}
\begin{align*}
  &C\expr{\ttt{runIter x}} := \ttt{TailRec $M\expr{\ttt{x}}$}\\
  &C\expr{\ttt{x + y}} := \ttt{Add $M\expr{\ttt{x}}$ $M\expr{\ttt{y}}$}\\
  &C\expr{\ttt{case scrutinee of \{ ... \}}} := \ttt{CaseExp $M\expr{\ttt{scrutinee}}$ } B\expr{\ttt{\{ ... \}}}\\
  &C\expr{\ttt{($\lambda$x $\rarr$ body)}} := A\expr{\lambda \ttt{x} \rarr \ttt{body}}\\
  &C\expr{\ttt{(f x)}} := \ttt{ConstructAp $M\expr{\ttt{f}}$ $M\expr{\ttt{x}}$}\;\;\;\;\text{(Where \ttt{f} is not a primitive or an application of a primitive)}\\
  &C\expr{\ttt{x}} := \ttt{Construct x}\;\;\;\;\text{(Where \ttt{x} is a variable which is not a primitive)}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} := \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} := \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} := \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} := \ttt{OneProdMatchExp }A\expr{\ttt{$\lambda$ x $\rarr$ body}}\\
  &P\expr{\ttt{ $\rarr$ body}} := \ttt{NullaryMatch $M\expr{\ttt{body}}$}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} := \ttt{Lam (Name @a uniq) $M\expr{\ttt{body$[\ttt{x} \mapsto \ttt{Var uniq}]$}}$}\text{\;\;\;\;\;(where \ttt{uniq} is a globally unique identifier)}\\
  &\\
  &M\expr{\ttt{(x :: a)}} :=
    \begin{cases}
      \ttt{externalize x} & \text{if}\; \nexists t, a\; \typeeq E\; t\\
      \ttt{x} & \text{if}\; \exists t, a\; \typeeq E\; t
    \end{cases}
\end{align*}

>>>>

\newcommand{\expr}[1]{(#1)} % Expression quasiquote
\newcommand{\rarr}{\rightarrow}
\newcommand{\Rarr}{\Rightarrow}
\newcommand{\rewrites}{\Longrightarrow}

@@

% \begin{tcolorbox}
%   \textbf{TODO}: Does this subsection use Oxford brackets in an appropriate way?
% \end{tcolorbox}

\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &\rewrites \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}
\end{align*}

\begin{align*}
  T'_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ case s of \{ ...$_A$ \}; ...$_B$ \}}}\\
    &\rewrites
        \ttt{\{ K x0 ... xN $\rarr$ $T_{\ttt{f}}\expr{\ttt{case s of \{ ...$_A$ \}}}$; $T'_{\ttt{f}}\expr{\ttt{\{ ...$_B$ \}}}$\}}\\
  T'_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}}\\
    &\rewrites
      \begin{cases}
        \ttt{\{ K x0 ... xN $\rarr$ body}[\ttt{f} \mapsto \ttt{Step}]\ttt{; }T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}\ttt{ \}} & \text{if \ttt{f} occurs free in \ttt{body}}\\
        \ttt{\{ K x0 ... xN $\rarr$ Done body; ... \}} & \text{otherwise}
      \end{cases}\\
  T'_{\ttt{f}}&\expr{\ttt{\{ \}}} \rewrites \ttt{\{ \}}\\
  T_{\ttt{f}}&\expr{\ttt{case s of \{ ... \}}}\\
    &\rewrites
      \begin{cases}
        \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{Done (case s of \{ ... \})} & \text{otherwise}
      \end{cases}
\end{align*}
\begin{align*}
  &C^{*}\expr{\ttt{x}} \rewrites
    \begin{cases}
      \ttt{x} & \text{if \ttt{x} has no subexpressions marked with \ttt{externalize}}\\
      C^{*}\expr{C\expr{\ttt{y}}} & \text{if \ttt{externalize y} is the first marked subexpression of \ttt{x}}\\
    \end{cases}\\
\end{align*}
\begin{align*}
  &C\expr{\ttt{runIter x}} \rewrites \ttt{TailRec $M\expr{\ttt{x}}$}\\
  &C\expr{\ttt{x + y}} \rewrites \ttt{Add $M\expr{\ttt{x}}$ $M\expr{\ttt{y}}$}\\
  &C\expr{\ttt{case scrutinee of \{ ... \}}} \rewrites \ttt{CaseExp $M\expr{\ttt{scrutinee}}$ } B\expr{\ttt{\{ ... \}}}\\
  &C\expr{\ttt{($\lambda$x $\rarr$ body)}} \rewrites A\expr{\lambda \ttt{x} \rarr \ttt{body}}\\
  &C\expr{\ttt{(f x)}} \rewrites \ttt{ConstructAp $M\expr{\ttt{f}}$ $M\expr{\ttt{x}}$}\;\;\;\;\text{(Where \ttt{f} is not a primitive or an application of a primitive)}\\
  &C\expr{\ttt{x}} \rewrites \ttt{Construct x}\;\;\;\;\text{(Where \ttt{x} is a variable which is not a primitive)}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} \rewrites \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} \rewrites \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} \rewrites \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} \rewrites \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} \rewrites \ttt{OneProdMatchExp }A\expr{\ttt{$\lambda$ x $\rarr$ body}}\\
  &P\expr{\ttt{ $\rarr$ body}} \rewrites \ttt{NullaryMatch $M\expr{\ttt{body}}$}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} \rewrites \ttt{Lam (Name @a uniq) $M\expr{\ttt{body$[\ttt{x} \mapsto \ttt{Var uniq}]$}}$}\text{\;\;\;\;\;(where \ttt{uniq} is a globally unique identifier)}\\
  &\\
  &M\expr{\ttt{(x :: a)}} \rewrites
    \begin{cases}
      \ttt{externalize x} & \text{if}\; \nexists t, a\; \typeeq E\; t\\
      \ttt{x} & \text{if}\; \exists t, a\; \typeeq E\; t
    \end{cases}
\end{align*}
